\newpage
\chapter{The OASIS3 configuration file {\it namcouple}}
\label{sec_namcouple}

The OASIS3 configuration file {\it namcouple} contains, below
pre-defined keywords, all user's
defined information necessary to configure a particular coupled
run. 

The {\it namcouple} is a text file with the following
characteristics:

\begin{itemize}
\item the keywords used to separate the information
can appear in any order;
\item the number of blanks between two character strings is
non-significant; 
\item all lines beginning with \# are ignored and considered as
comments.
\item {\bf blank lines are not allowed.}
\end{itemize}

The first part of {\it namcouple } is devoted to configuration of
general parameters such as the number of models involved in the
simulation, the number of fields, the communication technique, etc.
The second part gathers specific information on each coupling or I/O
field, e.g. their coupling period, the list of transformations or
interpolations to be performed by OASIS3 and associated
configuring lines (described in more details in chapter
\ref{sec_transformations}), etc.

Several {\it namcouple} inputs have been deprecated (become unsupported
or unused) in the current version,  but for backwards compatability, they are still 
allowed.  These inputs will be noted in the following text using the
notation ``UNUSED'' and not fully described.

In the next sections, a simple {\it namcouple} example is given and
all configuring parameters are described. The additional lines
containing the different parameters required for each transformation
are described in section \ref{sec_transformations}. An example of a
realistic {\it namcouple} can be found in 
{\tt
oasis3/examples/toyoasis3/input/} directory.
% XXX and {\tt
%/prism/util/running\break/adjunct\_files/oasis3/namcouple\_toyclim\_use}.

\section{An example of a simple {\it namcouple}}
\label{subsec_examplenamcouple}

The following simple {\it namcouple} configures a run in which an
ocean, an atmosphere and an atmospheric chemistry models are
coupled. The ocean provides only the SOSSTSST field to the atmosphere,
which in return provides the field CONSFTOT to the ocean. One field
(COSENHFL) is exchanged directly from the atmosphere to the
atmospheric chemistry, and one field (SOALBEDO) is read from a file by
the ocean.

\begin{verbatim}

######################################################################
# First section
#
 $SEQMODE
    1
#
 $CHANNEL
    MPI2    NOBSEND
    1    1   arg1
    3    1   arg2
    3    1   arg3            
#
 $NFIELDS
    4    9
#
 $JOBNAME
    JOB
#
 $NBMODEL
    3  ocemod   atmmod  chemod  55  70   99 
#
 $RUNTIME
    432000
#
 $INIDATE
    00010101
#
 $MODINFO
    NOT
#
 $NLOGPRT
   2
#
 $CALTYPE
   1
#
######################################################################
# Second section 
#
 $STRINGS
#
# Field 1
#
 SOSSTSST SISUTESU 1 86400  5  sstoc.nc  EXPORTED
 182  149  128  64  toce  atmo   LAG=+14400  SEQ=+1
 P 2 P 0
 LOCTRANS CHECKIN MAPPING  BLASNEW CHECKOUT 
#
  AVERAGE 
  INT=1
  map_toce_atmo_120315.nc src opt
  CONSTANT     273.15 
  INT=1
#
# Field 2
#
 CONSFTOT SOHEFLDO 6 86400  4   flxat.nc  EXPORTED
 atmo   toce  LAG=+14400  SEQ=+2
 P 0 P 2
 LOCTRANS  CHECKIN  MAPPING CHECKOUT
#
  ACCUMUL 
  INT=1
  map_atmo_toce_conserv.nc src opt
  INT=1
#
# Field 3
#
 COSENHFL  SOSENHFL  37  86400   1  flda3.nc  IGNOUT 
 atmo   atmo LAG=+7200 
 LOCTRANS
 AVERAGE
#
# Field 4
#
 SOALBEDO SOALBEDO  17  86400  0  SOALBEDO.nc  INPUT
#
#####################################################################
\end{verbatim}

%section{An example of a simple {\it namcouple}}

\section{ First section of {\it namcouple} file}
\label{subsec_namcouplefirst}

The first section of {\it namcouple } uses some predefined keywords
prefixed by the \$ sign to locate the related information. The
\$ sign must be in the second column. The first ten keywords
are described hereafter:

\begin{itemize}

\item {\tt \$SEQMODE}: UNUSED.  On the line below this keyword is an integer that plays no
role in the implementation in the current version.
  \ref{subsubsec_Algoritms}).

\item {\tt \$CHANNEL}: UNUSED.  On the line below this keyword should be the string
MPI1 but this plays no role in the implementation.
%On the line below this keyword is the
%communication technique chosen. Choices are {\tt MPI1} or {\tt MPI2}
%for the CLIM communication technique and related PSMILe library.  
%To run OASIS3 as an
%interpolator only, put {\tt NONE} (see also section
%\ref{subsec_interpolator}). 
%The communication techniques available in previous OASIS version, i.e.
%{\tt SIPC}, {\tt PIPE}, or {\tt GMEM} are not
%officially supported anymore.

%To use the {\tt CLIM/MPI2} communication technique, the lines below {\tt
%  \$CHANNEL} are, e.g. for 3 models:
%\begin{verbatim} 
%$CHANNEL 
%MPI2 NOBSEND
%1    1  arg1 
%3    1  arg2
%3    1  arg3 
%\end{verbatim}
%where {\tt MPI2} is the message passing used in CLIM and PSMILe, and
%{\tt NOBSEND} indicates that standard basic send {\tt MPI\_Send}
%should be used in place of the default buffered {\tt MPI\_BSend} to send the
%coupling fields. The standard basic send {\tt
%  MPI\_Send} can be used only if the coupling fields are sent and received in the same order
%by the different component models, i.e. the order into which they are listed in the 
%{\it namcouple}, or on platforms for which {\tt MPI\_Send} is
%implemented with a sufficiently large mailbox. The less efficient default
%buffered send {\tt MPI\_BSend} should be used on platforms for which {\tt MPI\_Send}
%is not implemented with a mailbox\footnote{Note that it was
%observed that the MPI\_Bsend does not work correctly on NEC SX8 with
%MPI libraries versions 7.2.0 et 7.2.1; this problem was solved with
%MPI version 7.2.4.} if the coupling fields are not sent
%and received in the order into which they are listed in the 
%{\it namcouple}\footnote{Note that below the call to {\tt
%  prism\_enddef\_proto}, the PSMILe tests whether or not the model has
%already attached to an MPI buffer. If it is the case, the PSMILe
%detaches from the buffer, adds the size of the pre-attached buffer to
%the size needed for the coupling exchanges, and reattaches to an MPI
%buffer. The model own call to {\tt MPI\_Buffer\_Attach} must therefore
%be done before the call to {\tt prism\_enddef\_proto}. Furthermore,
%the model is not allowed to call {\tt MPI\_BSend} after the call to
%{\tt prism\_terminate\_proto}, as the PSMILe definitively detaches
%from the MPI buffer in this routine. See the example in the atmoa3.F90
%model in {\tt oasis3/examples/toyoa3/atmoa3/src}.}. 
%
%The following lines (one line per model listed on the {\tt \$NBMODEL}
%line) indicate for each model the total number of processes, the
%number of processes implied in the coupling, and possibly launching
%arguments\footnote{The cases that have been fully tested are: 1- when all processes participate in the coupling; 2- when only the master process participate in the coupling. The case where a subset of more than one process participate in the coupling has not been tested.}. Here the first model runs on one process which is of course
%implied in the coupling and the argument passed to the model is
%"arg1"; the second and third models run on 3 processes but only one
%process is implied in the coupling (i.e. exchanging information with
%OASIS3 main process), and the argument passed to the models are
%respectively ``arg2" and ``arg3''.
%
%To use the {\tt CLIM/MPI1} communication technique, the {\tt
%  \$CHANNEL} lines are as for {\tt MPI2} except that {\tt MPI2} is
%replaced by {\tt MPI1} and there is no launching
%arguments. With MPI1, models have to be started by the user in
%  a pseudo-MPMD mode in the order they are introduced in the {\it
%    namcouple}. The way to do this depends on the computing platform.
%  With MPI1, OASIS3 main process and the component models
%  automatically share the same MPI\_COMM\_WORLD communicator; in this
%  communicator OASIS3 main process is assumed to have rank 0 and the
%  other component models are assumed to have ranks in the order of
%  which they are introduced in namcouple. If this is not the case, a
%  deadlock may occur.

\item {\tt \$NFIELDS}: On the line below this keyword is the total
number of fields exchanged and described in the second part of
the {\it namcouple}. 

\item {\tt \$JOBNAME}: On the line below this keyword is a {\tt
CHARACTER$\star$3} or {\tt CHARACTER$\star$4} variable giving an
acronym for the given simulation.

\item {\tt \$NBMODEL}: On the line below this keyword is the number of
models running in the given experiment followed by {\tt
CHARACTER$\star$6} variables giving their names, which must correspond to the name announced by each model when calling {\tt prism\_init\_comp\_proto} (second argument, see section \ref{subsubsec_Initialisation}). 

Then the user may
indicate the maximum Fortran unit number used by the models. In  the
example, Fortran units above 55, 70, and 99 are free for respectively
the ocean, atmosphere, and atmospheric chemistry models. If no
maximum unit numbers are indicated, OASIS3 PSMILe will suppose that units
above 1024 are free.  The unit number information is currently not used.
%If {\tt \$CHANNEL}
%is {\tt NONE}, {\tt \$NBMODEL} has to be 0 and there should be no
%model name and no unit number.

\item {\tt \$RUNTIME}: On the line below this keyword is the total
simulated time of the run, expressed in seconds. 
%If {\tt \$CHANNEL}
%is {\tt NONE}, {\tt \$RUNTIME} has to be the number of time occurrences
%of the field to interpolate from the restart file. 

\item {\tt \$INIDATE}: On the line below this keyword is the initial
  date of the run. The format is {\tt YYYYMMDD}. This date is important only
%  for the {\tt FILLING} transformation and 
  for printing information in OASIS3 log file {\it cplout}.

\item {\tt \$MODINFO}: UNUSED.  On the line below this keyword should
be the string NOT.
%  If coupling restart files are binary files (see
%  section \ref{subsec_restartdata}), the line below this keyword
%  indicates if a header is encapsulated or not: it can be {\tt
%  YES} or {\tt NOT}.
 
\item {\tt \$NLOGPRT}: The line below this keyword refers to the
  amount of information that will be written to the OASIS log files
  for each model and processor. The value of {\tt \$NLOGPRT} may be:  
  \begin{itemize}
  \item 0 : one file debug.root.xx is open by the master proces of each model and one file debug\_notroot.xx is open for all the other processes of each model to write error information.
  \item 1 : one file debug.root.xx is open by the master proces of each model to write information equivalent to level 10 (see below); one file debug\_notroot.xx is open for all the other processes of each model to write error information.
  \item 2 : one file debug.xx.xxxxxx is open by each process of each model to write normal production diagnostics
  \item 5 : as for 2 with in addition some initial debug info
  \item 10: as for 5 with in addition the routine calling tree
  \item 12: as for 10 with in addition some routine calling notes
  \item 15: as for 12 with even more debug diagnostics
  \item 20: as for 15 with in addition some extra runtime analysis
  \item 30: full debug information
 \end{itemize}
This value can be changed at runtime with the {\tt prism\_set\_debug} method.

\item {\tt \$CALTYPE}: UNUSED.  The line below this keyword contains
an integer that plays not role in the implementation.
%  This keyword gives the type of calendar
%  used. The calendar type is important only if {\tt FILLING}
%  analysis is used for a coupling field in the run and for printing
%  information in OASIS3 log file {\it cplout}. Below this keyword, a
%  number (0, 1 or n ) must be indicated by the user:
%  \begin{itemize}
%  \item 0 : a 365 day calendar (no leap year) 
%  \item 1 : a 365 or 366 (leap years) day calendar A year is a leap
%  year if it can be divided by 4; however if it can be divided by 4
%  and 100, it is not a leap year; furthermore, if it can be divided by
%  4, 100 and 400, it is a leap year.
%  \item n :  $n \ge 1$ day month calendar. 
%  \end{itemize}

\end{itemize}

%{Description of {\it namcouple} first section}

\section{Second section of {\it namcouple} file }
\label{subsec_namcouplesecond}

The second part of the {\it namcouple}, starting after the keyword
{\tt \$STRINGS}, contains coupling information for each coupling (or
I/O) field.  Its format depends on the field status given by the last
entry on the field first line ({\tt EXPORTED}, {\tt IGNOUT} or {\tt
INPUT} in the example above). The field may be :
%({\tt AUXILARY} and {\tt EXPORTED} are supported by all communication
%techniques, while the others are supported only by the PSMILe i.e. the
%{\tt CLIM/MPI1} or {\tt CLIM/MPI2} communication technique):

\begin{itemize}
\item {\tt AUXILARY}: UNUSED
%  sent by the source component, received and used by
%  OASIS3  for the transformation of other fields, but not sent to any target component.
\item {\tt EXPORTED}: exchanged between component models and
  transformed by OASIS3 .
\item {\tt EXPOUT}: exchanged, transformed and also written to two
  debug NetCDF files, one before the sending action in the source model
  below the {\tt prism\_put\_proto} call, and one after the receiving
  action in the target model below the {\tt prism\_get\_proto} call (should
  be used when debugging the coupled model only)
\item {\tt IGNORED}: this setting is equivalent to and converted to EXPORTED
\item {\tt IGNOUT}: this setting is equivalent to and converted to EXPOUT
\item {\tt INPUT}: simply read in from the input file by the target
  model PSMILe below the {\tt prism\_get\_proto} call at appropriate
  times corresponding to the input period indicated by the user in the
  {\it namcouple}. See section
  \ref{subsec_inputdata} for the format of the input file.
\item {\tt OUTPUT}: simply written out to an output file by the source
  model PSMILe below the {\tt prism\_put\_proto} call at appropriate
  times corresponding to the output period indicated by the user in
  the {\it namcouple}. The name of the output file (one per field) is
  automatically built based on the field name and initial date of the
  run ({\tt \$INIDATE}).

\end{itemize}

\subsection{Second section of {\it namcouple} for {\tt EXPORTED}, {\tt
      AUXILARY} and {\tt EXPOUT} fields}
\label{subsubsec_secondEXPORTED}

  The first 3 lines for fields with status {\tt EXPORTED} and 
  {\tt EXPOUT} are as follows:
  \begin{verbatim}
   SOSSTSST SISUTESU 1 86400  5  sstoc.nc  sstat.nc EXPORTED
   182  149    128  64  toce  atmo   LAG=+14400 SEQ=+1
   P 2 P 0 
  \end{verbatim}
  where the different entries are:
    \begin{itemize}
      \item Field first line:
        \begin{itemize}
        \item {\tt SOSSTSST} : symbolic name for the field in the
              source model ({\tt CHARACTER*8}). It has to match the
              argument {\tt name} of the corresponding field
              declaration in the source model; see {\tt
              prism\_def\_var\_proto} in section
              \ref{subsubsec_Declaration}.
        \item {\tt SISUTESU} : symbolic name for the field in the
              target model ({\tt CHARACTER*8}).  It has to match the
              argument {\tt name} of the corresponding field
              declaration in the target model; see {\tt
              prism\_def\_var\_proto} in section
              \ref{subsubsec_Declaration}.
        \item 1 : thie feature is not currently supported, but it is meant to be the
              index in auxiliary file cf\_name\_table.txt used by OASIS3 and PSMILe to 
              identify corresponding CF standard name and units (see \ref{subsec_cfnametable}).
        \item 86400 : coupling and/or I/O period for the field, in
        seconds. 
        \item 5 : number of transformations to be performed by OASIS3 on this field.  
        \item sstoc.nc : name of the coupling restart file for the
          field ({\tt CHARACTER*8}); 
          mandatory even if no coupling restart file is effectively
          used. (for more detail, see section \ref{subsec_restartdata});
        \item sstat.nc : UNUSED but still required for parsing
%          name of the field output file\footnote{In interplator-only mode (i.e. {\tt \$CHANNEL = NONE}), there must be one input file and one output file per field.}, may be indicated for
%	  {\tt NONE} (and {\tt PIPE}) communication techniques only. It
%	  may be a binary of netCDF file (see section
%	  \ref{subsec_restartdata}).
        \item {\tt EXPORTED} : field status.
        \end{itemize}
      \item Field second line:
        \begin{itemize}
        \item 182 : number of points for the source grid first
        dimension (optional if a netCDF coupling restart file is used). 
        \item 149 : number of points for the source grid second
        dimension (optional if a netCDF coupling restart file is used).    
        \item 128 : number of points for the target grid first
        dimension (optional if a netCDF coupling restart file is used). 
        \item 64 : number of points for the target grid second
        dimension (optional if a netCDF coupling restart file is used).  
        \item toce : prefix of the source grid name in grid data files (see section
        \ref{subsec_griddata}) ({\tt CHARACTER*4})
        \item atmo : prefix of the target grid name in grid data files
        ({\tt CHARACTER*4})
        \item {\tt LAG=+14400}: optional lag index for the field
        expressed in seconds 
        \item {\tt SEQ=+1}: optional sequence index for the field (see section  \ref{subsubsec_Algoritms})
        \end{itemize}
      \item Field third line
        \begin{itemize}
         \item P : source grid first dimension characteristic
            (`P': periodical; `R': regional).
         \item 2 : source grid first dimension number of overlapping grid points.
         \item P : target grid first dimension characteristic (`P':
         periodical; `R': regional).
         \item 0 : target grid first dimension number of overlapping grid points.
        \end{itemize}
     
      \end{itemize}
    
  The fourth line gives the list of transformations to be performed
  for this field. There is then one or more additional configuring lines
  describing some parameters for each transformation. These
  additional lines are described in more details in the chapter
  \ref{sec_transformations}.

%\subsection{Second section of {\it namcouple} for {\tt
%  IGNORED} and {\tt IGNOUT} fields}
%\label{subsubsec_secondIGNORED}
%  The first 2 lines for fields with status {\tt IGNORED} or {\tt
%  IGNOUT} are as follows:
%  \begin{verbatim}
%  COSENHFL SOSENHFL 37 86400 1 flda3.nc IGNOUT 
%  atmo   toce LAG=+7200\end{verbatim}
%  where the different
%  entries are as for {\tt EXPORTED} fields, except that there is no
%  output file name on the first line and no {\tt SEQ} index at the end
%  of the second line.
%
%  For {\tt IGNORED} fields, the name used in the coupling restart file
%  (if any) must be the target symbolic name.
%
%  The third line is {\tt LOCTRANS} if this transformation is chosen
%  for the field. Note that {\tt LOCTRANS} is the only transformation
%  supported for {\tt IGNORED}, {\tt IGNOUT} and {\tt OUTPUT} fields
%  (as it is performed directly in the PSMILe below the {\tt
%  prism\_put\_proto} call). If {\tt LOCTRANS} is chosen, a fourth line
%  giving the name of the time transformation is required. For more
%  detail on {\tt LOCTRANS}, see section \ref{subsec_timetrans}.

\subsection{Second section of {\it namcouple} for {\tt OUTPUT} fields}
\label{subsubsec_secondOUTPUT}
  The first 2 lines for fields with status {\tt OUTPUT} are as follows:
  \begin{verbatim}
  COSHFTOT  COSHFTOT   7   86400  0  fldhftot.nc OUTPUT 
  atmo   atmo \end{verbatim}
where the different entries are as for {\tt EXPOUT} fields, except
that the source symbolic name must be repeated twice on the field
first line, the restart file name is optional, there is no output file
name on the first line and no LAG or  SEQ index at the end of the second line.
The name of the output file is automatically determined by the PSMILe.

The third line is {\tt LOCTRANS} if this transformation is chosen for
the field. Note that {\tt LOCTRANS} is the only transformation
supported for {\tt OUTPUT} fields.

\subsection{Second section of {\it namcouple} for {\tt
  INPUT} fields}
\label{subsubsec_secondINPUT}

  The first and only line for fields with status {\tt INPUT} is:

  \begin{verbatim}
  SOALBEDO SOALBEDO  17  86400  0  SOALBEDO.nc  INPUT\end{verbatim} where the different entries are:
  \begin{itemize}
  \item  {\tt SOALBEDO}: symbolic name for the field in the target
  model ({\tt CHARACTER*8} repeated twice)
  \item 17:  index in auxiliary file cf\_name\_table.txt (see above for EXPORTED fields)
  \item 86400: input period in seconds
  \item 0: number of transformations (always 0 for {\tt INPUT} fields)
  \item {\tt SOALBEDO.nc}: {\tt CHARACTER*32} giving the input file
  name (for more detail on its format, see section
  \ref{subsec_inputdata})
  \item {\tt INPUT}: field status.
  \end{itemize}

