\newpage
\begin{thebibliography}{10}
\vspace{-0.3cm}
\bibitem[{Cassou et~al 1998}]{cassou}
Cassou, C., P.~Noyret, E.~Sevault, O.~Thual, L.~Terray, D.~Beaucourt, and
  M.~Imbard:
\newblock Distributed Ocean-Atmosphere Modelling and Sensitivity to the
  Coupling Flux Precision: the CATHODe Project.
\newblock {\em Monthly Weather Review}, 126, No 4: 1035-1053, 1998.

\bibitem[{Coquart et~al 2018}]{coquart 18}
Coquart, L., E.~Maisonnave, E. and S.~Valcke:
\newblock Using Open MP in OASIS3-MCT for the N-nearest-neighbor remapping
\newblock {\em Technical Report, WN/CMGC/18/19},  
\newblock CECI, Universit\'e de Toulouse, CNRS, Toulouse, France

\bibitem[{Craig et~al 2017}]{craig17}
Craig, A., S.~Valcke and L.~Coquart : 
\newblock Development and performance of a new version of the OASIS coupler, OASIS3-MCT\_3.0
\newblock {\em Geosci. Model Dev.}, 10: 3297--3308
\newblock https://doi.org/10.5194/gmd-10-3297-2017

\bibitem[{Craig et~al 2018}]{craig 18}
Craig, A., S.~Valcke: 
\newblock OASIS3-MCT4.0 Timing Study with MCT 2.10.beta1
\newblock {\em Technical Report, WN/CMGC/18/38},  
\newblock CECI, Universit\'e de Toulouse, CNRS, Toulouse, France

\bibitem[{Guilyardi et~al 1995}]{guily95}
Guilyardi, E., G.~Madec, L.~Terray, M.~D\'equ\'e, M.~Pontaud, M.~Imbard, D.~Stephenson, M.-A. ~Filiberti, D.~Cariolle, P.~Delecluse, and O.~Thual. 
\newblock Simulation coupl\'ee oc\'ean-atmosph\`ere de la variabilit\'e du climat.
\newblock {\em C.R. Acad. Sci. Paris}, t. 320, s\'erie IIa:683--690, 1995. 

\bibitem[{He and Ding 2001}]{He2001}
He, Y. and C.~H.~Q Ding.
\newblock Using Accurate Arithmetics to Improve Numerical Reproducibility and Stability in Numer- ical Applications.
\newblock The Journal of Supercomputing, 18, 259
\newblock https://doi.org/10.1023/A:1008153532043, 2001.

\bibitem[{Jacob et~al 2005}]{mct_jacob}
Jacob, R., J.~Larson, and E.~Ong:
\newblock MxN Communication and Parallel Interpolation in CCSM3 Using the Model Coupling Toolkit.
\newblock {\em Int. J. High Perf. Comp. App.}, 19(3), 293-307 2005

\bibitem[{Jones 1999}]{Jones99}
Jones, P.: 
\newblock Conservative remapping: First- and second-order conservative remapping.
\newblock Mon Weather Rev, 127, 2204-2210, 1999. 

\bibitem[{Larson et~al 2005}]{mct_larson} 
Larson, J., R.~Jacob, and E.~Ong:
\newblock The Model Coupling Toolkit: A New Fortran90 Toolkit for Building Multiphysics Parallel Coupled Models.
\newblock {\em Int. J. High Perf. Comp. App.}, 19(3), 277-292, 2005

\bibitem[{Mirin and Worley 2012}]{Mirin2012}
Mirin, A. A., and P.~H. Worley : 
\newblock Improving the Per- formance Scalability of the Community Atmosphere Model.
\newblock {\em Int. J. High Perf. Comp. App.}, 26, 17–30
\newblock https://doi.org/10.1177/1094342011412630, 2012.

\bibitem[{Noyret et~al 1994}]{noyret}
Noyret, P., E.~Sevault, L.~Terray and O.~Thual.
\newblock Ocean-atmosphere coupling. 
\newblock {\em Proceedings of the Fall Cray User Group (CUG) meeting},
1994.

\bibitem[{Piacentini et~al 2018}]{piacentini08}
Piacentini, A., E.~Maisonnave, G.~Jonville, L.~Coquart and S.~Valcke:
\newblock A parallel SCRIP interpolation library for OASIS, 
\newblock {\em Technical Report, WN/CMGC/18/34},  
\newblock CERFACS, Toulouse, France, 2018.

\bibitem[{Pontaud et~al 1995}]{pontaud}
Pontaud, M., L.~Terray, E.~Guilyardi, E.~Sevault, D.~B. Stephenson, and
  O.~Thual.
\newblock Coupled ocean-atmosphere modelling - computing and scientific
  aspects.
\newblock In {\em 2nd UNAM-CRAY supercomputing conference, Numerical
  simulations in the environmental and earth sciences}
\newblock Mexico-city, Mexico, 1995.

 \bibitem[{Sevault et~al 1995}]{clim2}
Sevault, E., P.~Noyret, and L.~Terray.
\newblock Clim 1.2 user guide and reference manual.
\newblock {\em Technical Report TR/CGMC/95-47}, CERFACS, 1995.

\bibitem[{Terray and Thual 1995b}]{clim1}
Terray, L. and O.~Thual.
\newblock Oasis: le couplage oc\'ean-atmosph\`ere.
\newblock {\em La M\'et\'eorologie}, 10:50--61, 1995.

\bibitem[{Terray and Thual 1993}]{terray1}
Terray, L. and O.~Thual.
\newblock Coupled ocean-atmosphere simulations. 
\newblock In {\em High Performance Computing in the Geosciences,
proceedings of the Les Houches Workshop}
\newblock F.X. Le Dimet Ed., Kluwer Academic Publishers B.V, 1993.

\bibitem[{Terray et~al 1995}]{clim3}
Terray, L., E.~Sevault, E.~Guilyardi and O.~Thual
\newblock OASIS 2.0 Ocean Atmosphere Sea Ice Soil User's Guide and Reference Manual
\newblock {\em Technical Report TR/CGMC/95-46}, CERFACS, 1995.

\bibitem[{Terray et~al 1995b}]{terray95}
Terray, L. O.~Thual, S.~Belamari, M.~D\'equ\'e, P.~Dandin, C.~L\'evy, and
P.~Delecluse. 
\newblock Climatology and interannual variability simulated by the arpege-opa
model. 
\newblock {\em Climate Dynamics}, 11:487--505, 1995

\bibitem[{Terray et~al 1999}]{terray3}
Terray, L., S.~Valcke and A.~Piacentini:
\newblock OASIS 2.3 Ocean Atmosphere Sea Ice Soil, User's Guide and
Reference Manual,
\newblock {\em Technical Report TR/CMGC/99-37}, 
\newblock CERFACS, Toulouse, France, 1999.

\bibitem[{Valcke et~al 2018}]{valcke11}
Valcke, S., L.~Coquart, A.~Craig, G.~Jonville, E.~Maisonnave, A.~Piacentini
\newblock Multithreaded or thread safe OASIS version including performance optimizations to adapt to many-core architectures, IS-ENES2 deliverable D2.3
\newblock {\em Technical Report, WN/CMGC/XX/XX},  
\newblock CERFACS, Toulouse, France, 2018.

\bibitem[{Valcke et~al 2017}]{valcke12}
Valcke, S., G.~Jonville, R.~Ford, M.~Hobson, A.~Porter and G.~Riley
\newblock Report on benchmark suite for evaluation of coupling strategies
\newblock {\em Technical Report, TR/CMGC/17/87},  
\newblock CERFACS, Toulouse, France, 2018.
\newblock http://cerfacs.fr/wp-content/uploads/2017/05/GLOBC-TR-IS-ENES2\_D10.3\_MAI2017.pdf

\bibitem[{Valcke et~al 2015}]{valcke10}
Valcke, S., T.~Craig, L.~Coquart: 
\newblock OASIS3-MCT User Guide, OASIS3-MCT 3.0, 
\newblock {\em Technical Report, WN/CMGC/15/38},  
\newblock CERFACS, Toulouse, France, 2010.

\bibitem[{Valcke 2013}]{valcke9}
Valcke, S.: 
\newblock The OASIS3 coupler: a European climate modelling community software
\newblock {\em Geosci. Model Dev.}, 6:373--388

\bibitem[{Valcke et~al 2013}]{valcke8}
Valcke, S., T.~Craig, L.~Coquart: 
\newblock OASIS3-MCT User Guide, OASIS3-MCT 2.0, 
\newblock {\em Technical Report, WN/CMGC/13/17},  
\newblock CERFACS, Toulouse, France, 2013.

\bibitem[{Valcke et~al 2012}]{valcke7}
Valcke, S., T.~Craig, L.~Coquart: 
\newblock OASIS3-MCT User Guide, OASIS3-MCT 1.0, 
\newblock {\em Technical Report, WN/CMGC/12/49},  
\newblock CERFACS, Toulouse, France, 2012.

\bibitem[{Valcke et~al 2011}]{valcke6}
Valcke, S., M.~Hanke, L.~Coquart:
\newblock OASIS4\_1 User Guide
\newblock {\em Technical Report TR/CMGC/11/50}, 
\newblock CERFACS, Toulouse, France, 2011. 

\bibitem[{Valcke 2006b}]{valcke5}
Valcke, S.: 
\newblock OASIS3 User Guide (prism\_2-5) 
\newblock {\em Technical Report TR/CMGC/06/73}, 
\newblock CERFACS, Toulouse, France, 2006. 

\bibitem[{Valcke 2006a}]{valcke4}
Valcke, S.: 
\newblock OASIS4 User Guide (OASIS4\_0\_2), 
\newblock {\em Technical Report TR/CMGC/06/74}, 
\newblock CERFACS, Toulouse, France, 2006. 

\bibitem[{Valcke et~al 2004}]{valcke3}
Valcke, S., A.~Caubel, R.~Vogelsang, and D.~Declat:       
\newblock OASIS3 User's Guide (oasis3\_prism\_2-4),
\newblock {\em PRISM Report No 2, 5th Ed.}, 
\newblock CERFACS, Toulouse, France, 2004.

\bibitem[{Valcke et~al 2003}]{valcke2}
Valcke, S., A.~Caubel, D.~Declat and L.~Terray:        
\newblock OASIS3 Ocean Atmosphere Sea Ice Soil User's Guide,
\newblock {\em Technical Report TR/CMGC/03-69}, 
\newblock CERFACS, Toulouse, France, 2003.

\bibitem[{Valcke et~al 2000}]{valcke1}
Valcke, S., L.~Terray and A.~Piacentini:
\newblock OASIS 2.4 Ocean Atmosphere Sea Ice Soil, User's Guide and
Reference Manual,
\newblock {\em Technical Report TR/CMGC/00-10}, 
\newblock CERFACS, Toulouse, France, 2000.

\end{thebibliography}
